Inverse energy transfer in three-dimensional quantum vortex flows

### 2025-11-10 revision-2/referee-response.tex

\refcomment{The finding of inverse energy transfer by single reconnection is
interesting. However, other events cause forward energy transfer of
normal fluid, e.g., nonlinear interaction, wake propagation, energy
dissipations by mutual friction and viscosity, and so on. Therefore,
it is unclear whether the inverse energy cascade of normal fluid is
generated by reconnections in quantum turbulence. This stage is
premature to recommend to Physical Review Letters.}

\CHANGE{We think that by including the data regarding Hopf-link reconnections, we generalised our findings beyond a particular type of reconnection. This inverse energy transfer,
triggered by classical-like phenomena (chiral imbalance, which as in classical turbulence produces energy flowing towards large scales), is strikingly dissimilar from 
the direct energy transfer observed in vortex reconnections occurring in classical viscous fluids. Our work shows that vortex reconnections in quantum fluids may possess 
different characteristics from the ones taking place in classical fluids, depending on the fluid component we focus on: if we analyse superfluid vortices, the approach and 
separation is akin to classical dynamics (see our recent work, Stasiak et al., PNAS Vol. 122 No. 21 e2426064122 (2025)); if we observe the normal fluid we observe a non-classical 
energy transfer. Furthermore, this work adds additional elements to the lively discussion in the community regarding similarities and differences between classical and quantum 
turbulence. We think that together with the suggestion that reconnections may trigger an inverse energy cascade, these are the main findings of our investigation, which are of 
relevance for a broad audience such as PRL's readers. We have slightly changed the conclusions to emphasise these aspects.}

\subsection*{Referee B}

We thank the Referee for reading our revised version. We would like to insist, as it seems that is has not yet realized by the Referee, that our work is not about explaining the findings of Polanco and Krstulovic about the inverse cascade observed in that work for high counterflow. We have only mentioned that there might be a connection, but no claim is made. As a matter of fact, the comment is mild and we suggest that further studies are needed, so we open an new possible avenue of research. We have not mentioned such a claim in the abstract and not even in the introduction.

The referee make a claim that on head-on collision of quantum rings. We believe that the Referee is missing an important point. One could perhaps find a specific configuration such that the helicity imbalance is weaken or even suppressed. However, our point is that such is not the generic case, and it will not be relevant for experiments in quantum turbulence. The Referee should notice that in the orthogonal reconnection, discussed in the first version of our paper, the helicity for each pair is zero. In this revised version, we have included around 50 new reconnections of a Hopf-Link, which are topologically very different as the vortex filaments do have a non-zero initial helicity. The simulations of the Hopf-Link reproduce what we have observed with the orthogonal reconnection. We thus conclude, that our fining are robust and generic and physically relevant.

### 2025-11-10 main_REV.tex
GK corrections

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand*{\NOTE}[1]{\textbf{\color{red}[#1]}}
\newcommand*{\CHANGE}[1]{{\color{magenta}#1}}
\newcommand*{\DEL}[1]{{\color{green}#1}}

@@

\begin{abstract}
Vortex reconnections play a fundamental role in fluids.
% and they are typically considered as a mechanism to 
They increase the complexity of flow and develop small-scale motions.
In this work, we report that in superfluids, they can also excite large scales.
We numerically illustrate that during a superfluid vortex reconnection energy 
is injected 
into the thermal (normal) component of helium~II at small length scales, but is transferred nonlinearly  to larger length scales, 
increasing the integral length scale of the normal fluid.  
We show that this inverse energy transfer is triggered by the helical imbalance generated 
%at reconnection 
in the normal fluid flow by
the mutual friction force coupling the superfluid vortices and the normal component. We finally discuss
%by decomposing the velocity and the mutual friction (which couples superfluid and normal fluid) into helical modes, showing 
%that the imbalance of homochiral modes results from the punctuated energy and helicity injection during the reconnection. Finally, we discuss 
the relevance of our findings to 
the problem of superfluid turbulence.
\end{abstract}

@@

To study the reconnection dynamics, we consider 
\CHANGE{
two distinct initial conditions at temperatures $T=1.9K$ and $T=2.1K$: (a) a pair of initially orthogonal vortices (a second pair of orthogonal vortices, with
corresponding vortices of each pair having opposite circulation, is included in the computation in order to preserve periodicity along the boundaries \cite{suppMat};  
the vortex pairs are separated by the distance $D_{\ell}$, while each vortex within each pair is initially at distance $d_{\ell}$ to the other vortex, such that $d_{\ell}\ll D_{\ell}$ in order to ensure that the dynamics in the vicinity of the reconnection is dominated by local interactions); (b) a set of 49 Hopf-links, 
each consisting in two, perpendicular, linked vortex rings at varying initial distances from each other \cite{suppMat}.
}

@@

%\paragraph*{Closing remarks.---}
In conclusion, the reconnection of quantum vortices in the two-fluid regime
($T\gtrsim 1.5$K) not only injects punctuated
energy in the normal fluid \cite{stasiak2025experimental}, but also triggers in the normal fluid
a transfer of kinetic energy towards the large scales. 
%This inverse 
%energy transfer arises from the fact that the mutual friction force (injecting energy and 
%helicity in the normal fluid) is helical, as Kelvin waves develop on the vortices as a result of the reconnection itself.
%The helical character of the mutual friction produces a chiral imbalance in the normal fluid, driving this inverse transfer, as previously observed in turbulent Navier-Stokes flows
This inverse energy transfer is triggered by the helical character of the
mutual friction, directly arising from the Kelvin waves released by the reconnecting
cusp, which produces a chiral imbalance in the normal fluid, as 
previously observed in turbulent Navier-Stokes flows
\cite{biferaleInverseEnergyCascade2012a,plunianInverseCascadeEnergy2020a}.
\CHANGE{
This inverse energy transfer contrasts with the direct energy transfer observed 
in classical vortex reconnections \cite{yao-hussain-2020} showing that vortex reconnections 
in quantum fluids may show similarities and differences with their classical counterpart 
depending on the fluid component investigated: if we consider the approach and separation 
of superfluid vortex filaments, we recover a classical behaviour
\cite{stasiak2025experimental}, while if we analyse the normal fluid energy transfer we
observe a strong non-classical effect. The results presented hence contribute to 
identifying similarities and differences between classical and quantum turbulence 
\cite{galantucci-2025}. 
}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand*{\NOTE}[1]{\textbf{\color{red}[#1]}}
\newcommand*{\CHANGE}[1]{{\color{magenta}#1}}
\newcommand*{\GK}[1]{{\color{blue}#1}}
\newcommand*{\DEL}[1]{{\color{green}#1}}

@@

\begin{abstract}
Vortex reconnections play a fundamental role in fluids.
% and they are typically considered as a mechanism to 
They increase the complexity of flow and develop small-scale motions.
In this work, we report that in superfluids, they can also excite large scales.
We numerically illustrate that during a superfluid vortex reconnection energy 
is injected into the thermal (normal) component of helium~II at small length scales, but is transferred nonlinearly  to larger length scales, increasing the integral length scale of the normal fluid. 
We show, \GK{by studying about fifty different reconnections,} that this inverse energy transfer is triggered by the helical imbalance generated 
%at reconnection 
in the normal fluid flow by
the mutual friction force coupling the superfluid vortices and the normal component. 
We finally discuss
%by decomposing the velocity and the mutual friction (which couples superfluid and normal fluid) into helical modes, showing 
%that the imbalance of homochiral modes results from the punctuated energy and helicity injection during the reconnection. Finally, we discuss 
the relevance of our findings to 
the problem of superfluid turbulence.
\end{abstract}

@@

To study the reconnection dynamics, we consider 
\CHANGE{
two distinct initial conditions at temperatures $T=1.9K$ and $T=2.1K$: (a) a pair of initially orthogonal vortices (a second pair of orthogonal vortices, with
corresponding vortices of each pair having opposite circulation, is included in the computation in order to preserve periodicity along the boundaries \cite{suppMat};  
the vortex pairs are separated by the distance $D_{\ell}$, while each vortex within each pair is initially at distance $d_{\ell}$ to the other vortex, such that $d_{\ell}\ll D_{\ell}$ in order to ensure that the dynamics in the vicinity of the reconnection is dominated by local interactions); (b) a set of 49 Hopf-links, 
each consisting in two, perpendicular, linked vortex rings at varying initial distances from each other \cite{suppMat}.
}\GK{Note that the two types of initial conditions are topologically very different, as for the Hopf-Link the superfluid initial helicity is non-zero due to their linking (it is zero for the orthogonal case). For both configurations, the initial normal fluid helicity is zero.}

@@

%\paragraph*{Closing remarks.---}
In conclusion, the reconnection of quantum vortices in the two-fluid regime
($T\gtrsim 1.5$K) not only injects punctuated
energy in the normal fluid \cite{stasiak2025experimental}, but also triggers in the normal fluid
a transfer of kinetic energy towards the large scales. 
%This inverse 
%energy transfer arises from the fact that the mutual friction force (injecting energy and 
%helicity in the normal fluid) is helical, as Kelvin waves develop on the vortices as a result of the reconnection itself.
%The helical character of the mutual friction produces a chiral imbalance in the normal fluid, driving this inverse transfer, as previously observed in turbulent Navier-Stokes flows
This inverse energy transfer is triggered by the helical character of the
mutual friction, directly arising from the Kelvin waves released by the reconnecting
cusp, which produces a chiral imbalance in the normal fluid, as 
previously observed in turbulent Navier-Stokes flows
\cite{biferaleInverseEnergyCascade2012a,plunianInverseCascadeEnergy2020a}.
\CHANGE{
This inverse energy transfer contrasts with the direct energy transfer observed 
in classical vortex reconnections \cite{yao-hussain-2020} showing that vortex reconnections 
in quantum fluids may show similarities and differences with their classical counterpart 
depending on the fluid component investigated: if we consider the approach and separation 
of superfluid vortex filaments, we recover a classical behaviour
\cite{stasiak2025experimental}, while if we analyse the normal fluid energy transfer we
observe a strong non-classical effect. \GK{The robusteness of our results has been demonstrated by studying almost fifty different reconnections having an initial different topology.} The results presented hence contribute to 
identifying similarities and differences between classical and quantum turbulence 
\cite{galantucci-2025}. 
}
